Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-14 paper/paper.tex
orgnanizing the structure and making another pass on some sections

\keywords{JavaScript, Diversity, Software Testing}

@@

\section{Objects of Study}
\label{sec:methodology}

This section discusses the objects we used in our study.

\subsection{Engines}
\label{sec:methodology:engines}~We selected 
JS engines according to the following criteria.

\begin{itemize}
\item Released latest version after Jan 1, 2018
\item Contains more than 1K stars on GitHub  
\item Uses a public issue tracker
\end{itemize}

We look for highly-maintained (as per the first criterion) and popular
(as per the second criterion) projects. As we wanted to report bugs,
we also looked for project with public issue
trackers. Table~\ref{tab:engines} lists the engines we analyzed in
this work. It is worth noting that we used GoogleChromeLab's JSVU
tool~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:engines}Engines analyzed.}
  \begin{tabular}{cccrr}
    \toprule
    Team & Name & URL & \# Stars  & DOB \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
    \multicolumn{1}{c}{3300+} & Jun 2001\\
    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
    \multicolumn{1}{c}{1100+} & Mar 1996\\
   \bottomrule     
  \end{tabular}
\end{table}

\subsection{Seed JS files\label{sec:seeds}}~
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files from the suites
of public engines, and 4) test files mined from issue trackers of
these engines.

@@

Table~\ref{tab:test-suites} shows the breakdown of tests we per
engine. Column ``original'' shows the number of test cases associated
with each test suite. Column ``pass-in-par.''  shows the number of
test cases that pass in their parent engine. We discarded tests that
fail in their parent engine as we could not reliably indicate the
reason for the failure, so we assumed the test could be broken. We
removed 63 test cases that fail for that reason--6 tests from \jsc{}
and 57 tests from \smonkey. Column ``compile-in-all'' shows the number
of test cases whose executions do not throw dynamic type errors in any
of the engines because of an undefined variable or property. We
capture these cases by looking for the presence of
\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
when test execution attempts to access an undefined variable
(respectively, property of an object). We discarded those tests to
avoid noise in the experiments as they clearly indicate some missing
feature as opposed to bugs. For example, some tests use non-portable
names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. We used the
\totalTestFilesForTestTransplantation{} tests included in the circle
from the table in the evaluation of test transplantation, \ie{}, all
tests under the ``compile-in-all'' column\Mar{change name to
  type-in-all} but the Test262 tests. We did not consider tests from
the conformance suite as they are more likely to indicate missing
features as opposed to bugs. In addition, engine developers have
access to these test and are encouraged to run them.  Column
``no-fail-in-all'' shows the tests for which all engines pass. This
test set is used in the evaluation of differential testing. Note that
it is a proper subset of the ``compile-in-all'' test set. The tests
from this group are used as fuzzing seeds. The guarantee that they
pass in all engines assures that, if discrepancies occur, they are
related to the changes in the input as opposed to the original cause
of failure.

@@

\subsubsection{Mining Tests from Issue Trackers}

@@

\newcommand\marktopleft[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-a) at (0,1.5ex) {};%
}
\newcommand\markbottomright[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-b) at (0,0) {};%
    \tikz[overlay,remember picture,thick,dashed,inner sep=3pt]
        \node[draw,rounded rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
}

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.\Mar{explain
      ``pass-in-par.''}\Mar{why SpiderMonkey 1,977->2,116?}}
  \setlength{\tabcolsep}{2.25pt}      
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & original & pass-in-par. & compile-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & 17,639 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,025 &\marktopleft{c1}1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 1,977 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

@@

\section{Differential Testing Infrastructure}
\label{sec:design}

\begin{figure}[h!]
  \centering
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
\end{figure}

\begin{figure}[!h]
  \centering
  \begin{lstlisting}
var buffer = new ArrayBuffer(64);
var view = new DataView(buffer);
view.setInt8(0,0x80);
assert(view.getInt8(-1770523502845470856) === -0x80);

\Fix{reviewer asks for more details...}

@@

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
code snippet below shows the test input we used to reveal a bug in
\chakra.

@@

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}  The
code snippet below shows the test input we used to reveal a bug in
\veight{}.

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assert, assertEq, var, yield, in, function, eval,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
 eval(function b (a) { break;});
  \end{lstlisting}
  \normalsize
  %% \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
  %% and reported in \veight{} engine}
\end{figure}

This code snippet was obtained by fuzzing a Test262 test with
\quickfuzz. In its original version, a string (omitted for space),
passed as argument to the \CodeIn{eval} function, encoded the actual
test. The fuzzer replaced the string argument with a function whose
body is a \CodeIn{break} statement outside a valid block
statement. Section B.3.3.3 from the spec~\cite{spec-b333} documents
how eval should handle code containing function declarations.
According to the spec~\cite{break-statement}, the virtual machine
should throw an early error--in this case, a SyntaxError--if the break
statement is not nested in an iterable or a switch statement. In this
case, all engines, but \veight{}, behave as expected.

>>>>

%% \keywords{JavaScript, Diversity, Software Testing}

@@

%% \section{Objects of Study}
%% This section discusses the objects we used in our study.

\section{Engines Studied}
\label{sec:methodology}
\label{sec:methodology:engines}~We selected 
JS engines according to the following criteria: 1) Released latest
version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
and 3) Uses a public issue tracker. We looked for highly-maintained
(as per the first criterion) and popular (as per the second criterion)
engines. As we wanted to report bugs, we also looked for project with
public issue trackers. Table~\ref{tab:engines} lists the engines we
analyzed. It is worth noting that we used GoogleChromeLab's JSVU
tool~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:engines}Engines selected.}
  \begin{tabular}{cccrr}
    \toprule
    Team & Name & URL & \# Stars  & DOB \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
    \multicolumn{1}{c}{3300+} & Jun 2001\\
    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
    \multicolumn{1}{c}{1100+} & Mar 1996\\
   \bottomrule     
  \end{tabular}
\end{table}

\section{Seed JS files}
\label{sec:seeds}
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files from the suites
of public engines, and 4) test files mined from issue trackers of
these engines.

@@

Table~\ref{tab:test-suites} shows the breakdown of tests we per
engine. Column ``full'' shows the number of test cases associated
with each engine. Column ``pass-in-par.''  shows the number of
test cases that pass in their parent engine. We discarded tests that
fail in their parent engine as we could not reliably indicate the
reason for the failure, so we assumed the test could be broken. We
removed 63 test cases that fail for that reason--6 tests from \jsc{}
and 57 tests from \smonkey. Column ``type-in-all'' shows the number
of test cases whose executions do not throw dynamic type errors in any
of the engines because of an undefined variable or property. We
capture these cases by looking for the presence of
\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
when test execution attempts to access an undefined variable
(respectively, property of an object). We discarded those tests to
avoid noise in the experiments as they clearly indicate some missing
feature as opposed to bugs. For example, some tests use non-portable
names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. We used the
\totalTestFilesForTestTransplantation{} tests included in the circle
from the table in the evaluation of test transplantation, \ie{}, all
tests under the ``type-in-all'' column\Mar{change name to
  type-in-all} but the Test262 tests. We did not consider tests from
the conformance suite as they are more likely to indicate missing
features as opposed to bugs. In addition, engine developers have
access to these test and are encouraged to run them.  Column
``no-fail-in-all'' shows the tests for which all engines pass. This
test set is used in the evaluation of differential testing. Note that
it is a proper subset of the ``type-in-all'' test set. The tests
from this group are used as fuzzing seeds. The guarantee that they
pass in all engines assures that, if discrepancies occur, they are
related to the changes in the input as opposed to the original cause
of failure.

\newcommand\marktopleft[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-a) at (0,2ex) {};%
}
\newcommand\markbottomright[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-b) at (0,0) {};%
    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
        \node[draw,rounded rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
}

%% \Comment{ Column ``full'' shows the number of the test cases found
%%     for that engine, column ``compile-in-all'' shows the number of
%%     test cases for which engines do not throw compile error (\eg{},
%%     undefined name), and column ``no-fail-all'' shows the number of
%%     test cases that pass in all four engines we analyzed.\Mar{explain
%%       ``pass-in-par.''}\Mar{why SpiderMonkey 1,977->2,116?}}}

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test cases per suite.}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & 17,639 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,025 &\marktopleft{c1}1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 1,977 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

@@

\subsection{Mining Tests from Issue Trackers}

@@

\section{Cross-Engine Differential Testing}
\label{sec:design}

\begin{figure}[t]
  \centering
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
\end{figure}

\begin{figure}[t!]
  \centering
  \begin{lstlisting}
var buffer = new ArrayBuffer(64);
var view = new DataView(buffer);
view.setInt8(0,0x80);
assert(view.getInt8(-1770523502845470856) === -0x80);

\Fix{...reviewer asks for more details...check what we added in the
  rebuttal for this.}

@@

@@

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
code snippet below shows a test that reveals a bug in \chakra.

@@

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}  The
code {\footnotesize\ttfamily{eval(function b(a)\{break;\});}} shows
the test input we used to reveal a bug in \veight{}. This code snippet
was obtained by fuzzing a Test262 test with \quickfuzz. In its
original version, a string (omitted for space), passed as argument to
the \CodeIn{eval} function, encoded the actual test. The fuzzer
replaced the string argument with a function whose body is a
\CodeIn{break} statement outside a valid block statement. Section
B.3.3.3 from the spec~\cite{spec-b333} documents how eval should
handle code containing function declarations.  According to the
spec~\cite{break-statement}, the virtual machine should throw an early
error--in this case, a SyntaxError--if the break statement is not
nested in an iterable or a switch statement. All engines, but
\veight{}, behave as expected in this case.
